---
title: "DIVI Intensivregister Report"
output: html_notebook
---

In diesem Skript wird die Belegung der Intensivbetten nach dem DIVI-Intensivregister ausgegeben
Mehr Informationen finden sich hier: https://www.divi.de/register/tagesreport

```{r}
# Es wird mittels API auf die Daten zugegriffen

library(rjson)
library(plyr)
library(dplyr)
library(ggplot2)
library(jsonlite)
library(tidyverse)

ags <- "09182" #Festlegen des allgemeinen Gemeindeschlüssels, 09182 ist Miesbach
divi_tagesreport_csv_link <- paste0("https://www.divi.de/joomlatools-files/docman-files/divi-intensivregister-tagesreports-csv/DIVI-Intensivregister_2021-",format(Sys.Date(),"%m-%d"),"_12-15.csv")

raw_tagesreport_csv <- read.csv(file=divi_tagesreport_csv_link)
raw_tagesreport_csv$gemeindeschluessel <- paste0("0", raw_tagesreport_csv$gemeindeschluessel)
tagesreport_aktueller_lkr <- raw_tagesreport_csv[raw_tagesreport_csv$gemeindeschluessel==ags,]

raw_intensivregister <- rjson::fromJSON(file = "https://www.intensivregister.de/api/public/intensivregister", method='C')


get_png <- function(filename) {
  grid::rasterGrob(png::readPNG(filename), interpolate = TRUE)
}

background_divi <- get_png("dashboard-app/background-divi.png")

dat <- data.frame(
  value = c(20, 30, 30, 40),
  posx = c(0, 10),
  posy = c(0, 10)
)

format(as.POSIXct(tagesreport_aktueller_lkr$daten_stand), "%d.%m.%Y um %H:%M Uhr")

divi_label_total <- data.frame(
  value = c(paste0(tagesreport_aktueller_lkr$betten_frei), 
            paste0(tagesreport_aktueller_lkr$betten_belegt), 
            paste0(tagesreport_aktueller_lkr$faelle_covid_aktuell), 
            paste0(tagesreport_aktueller_lkr$faelle_covid_aktuell_beatmet)),
  posx = c(0.7, 3.5, 6.4, 9.2),
  posy = c(4.7, 4.7, 4.7, 4.7)
)

divi_title_label <-  data.frame(
  value = c(paste("Daten DIVI-Intensivregister für Gemeindeschlüssel ", tagesreport_aktueller_lkr$gemeindeschluessel)),
  posx = c(4.4),
  posy = c(9.5)
)

divi_disclaimer_label <-  data.frame(
  value = c(paste("DIVI Intensivregister, Datenstand: ", format(as.POSIXct(tagesreport_aktueller_lkr$daten_stand), "%d.%m.%Y um %H:%M Uhr"))),
  posx = c(2.6),
  posy = c(1.7)
)

ggplot(dat, aes(x=posx, y=posy)) +
  geom_line(color = "white") +
  annotation_custom(background_divi, -Inf, Inf, -Inf, Inf) +
  geom_text(data = divi_title_label, aes(label=value), show.legend = FALSE, size=5) +
  geom_text(data = divi_label_total, aes(label=value), show.legend = FALSE, size=6) +
  geom_text(data = divi_disclaimer_label, aes(label=value), show.legend = FALSE, size=4) +
  theme_void() +
  theme(aspect.ratio = 10/30)


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
# intensivregister <- raw_intensivregister$data
# intensivregister_flat <- purrr::flatten(intensivregister)
# 
# 
# intensivregister_df <- intensivregister %>%
# 
#     # make json, then make list
#     toJSON() %>%
#     fromJSON() %>%
# 
#     # remove classification level
#     purrr::flatten() %>%
# 
#     # turn nested lists into dataframes
#     map_if(is_list, as_tibble) %>%
# 
#     # bind_cols needs tibbles to be in lists
#     map_if(is_tibble, list) %>%
# 
#     # creates nested dataframe
#     bind_cols()
# 
# 
# 
# intensivregister <- ldply(intensivregister, data.frame)
# ldply(intensivregister, data.frame)
```

